Investigating Bicycle Theft in Toronto: Trends and Patterns

### 2024-09-26 paper/paper.qmd
Edited cleaned dataset and some graphs in paper

```{r}
#| label: fig-occur
#| fig-cap: Number of bicycle theft incidents
#| warning: false
#| message: false
#| echo: false

date_counts <- as.data.frame(table(data$occ_date))
colnames(date_counts) <- c("date", "count")
date_counts|>
  ggplot(aes(x = as.Date(date), y = count)) +
  geom_line() +
  theme_minimal() +
  labs(x = "Date", y = "Number of Occurrences")

@@

```{r}
#| label: fig-crime-scenes
#| fig-cap: Number of occurrences categorized by crime scene
#| echo: false
#| warning: false
#| message: false
data |>
  ggplot(mapping = aes(x=occ_year, fill = premises_type)) + 
  geom_bar(position = "dodge2") +
  labs(x = "Year", y = "Number of Occurrences", fill = "Types of Crime Scenes") +
  theme(legend.position = "bottom")

@@

The original dataset includes a variable for the price of stolen bicycles, but it does not contain a variable for grouped prices. Therefore, I created a new variable called cost_group by grouping the prices in increments of $500. @fig-stolen-bike shows a bar graph with number of bike stolen by year categorized by cost group. From 2020 to 2022, the thefts of relatively inexpensive bicycles, priced under $1,000, have significantly decreased. On the other hand, high-end bicycles priced over $2,000 were stolen about 250 times in 2014. But this number has steadily increased, reaching approximately 500 thefts by 2022.
```{r}
#| label: fig-stolen-bike
#| fig-cap: Total cost of bicycle by year
#| fig-pos: "H"
#| echo: false
#| warning: false
#| message: false
data |>
  ggplot(mapping = aes(x=occ_year, fill = cost_group)) + 
  geom_bar(position = "dodge2") +
  labs(x = "Year", y = "Cost of Bicycle", fill = "Cost Group") +
  theme(legend.position = "bottom")

>>>>

```{r}
#| label: fig-occur
#| fig-cap: Number of bicycle theft incidents
#| warning: false
#| message: false
#| echo: false
#| layout-ncol: 2

date_counts <- data |>
  group_by(occ_year) |>
  summarise(total_occurrences = n())

ggplot(date_counts, mapping = aes(x = occ_year, y = total_occurrences)) +
  geom_line() +
  theme_minimal() +
  labs(x = "Date", y = "Number of Occurrences")

date_counts |>
  slice(1:10) |>
  kable(
    digits = 4,
    booktabs = TRUE,
    linesep = ""
  )

@@

```{r}
#| label: fig-crime-scenes
#| fig-cap: Number of occurrences categorized by crime scene
#| echo: false
#| warning: false
#| message: false
data |>
  ggplot(mapping = aes(x=occ_year, fill = premises_type)) + 
  geom_bar(position = "dodge2") +
  facet_wrap(~ premises_type) +
  labs(x = "Year", y = "Number of Occurrences", fill = "Types of Crime Scenes") +
  theme(
    legend.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.key.size = unit(0.4, "cm"),legend.position = "bottom"
    )

@@

The original dataset includes a variable for the price of stolen bicycles, but it does not contain a variable for grouped prices. Therefore, I created a new variable called cost_group by grouping the prices in increments of $500. @fig-stolen-bike shows a bar graph with number of bike stolen by year categorized by cost group. From 2020 to 2022, the thefts of relatively inexpensive bicycles, priced under $1,000, have significantly decreased. On the other hand, high-end bicycles priced over $2,000 were stolen about 250 times in 2014. But this number has steadily increased, reaching approximately 500 thefts by 2022.
```{r}
#| label: fig-stolen-bike
#| fig-cap: Total cost of bicycle by year
#| fig-pos: "H"
#| echo: false
#| warning: false
#| message: false

data <-
  data|>mutate(
  cost_group =
      factor(cost_group, levels = c("< $500", "$500 < $1000", "$1000 < $1500", "$1500 < $2000", "$2000 <")))
data |>
  ggplot(mapping = aes(x=occ_year, fill = cost_group)) + 
  geom_bar() +
  facet_wrap(~ cost_group) +
  labs(x = "Year", y = "Cost of Bicycle", fill = "Cost Group") +
  theme(
    legend.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.key.size = unit(0.4, "cm"),
    legend.position = "bottom"
  )
```

```{r}
